\begin{abstract}
We present \sys, a system for the discovery of declarative rules over knowledge-bases (KBs).
\sys does not limit its search space to rules that rely on ``positive'' relationships between entities, such as ``if two persons have the same parent, they are siblings'', as in traditional mining of constraints for KBs. On the contrary, it extends the search space to discover also negative rules, i.e., patters that lead to contradictions in the data, such as ``if two person are married, one cannot be the child of the other". While the former class is fundamental to infer new relationships in the KB, the latter class is crucial for error detection in data cleaning, or for the creation of negative examples when bootstrapping learning algorithms.

The main technical challenges addressed in this paper consist in enlarging the expressive power of the considered rules to include comparison among constants, including disequalities, and in designing a disk-based discovery algorithm, effectively dropping the assumption that the KB has to fit in memory to have acceptable performance. 
To guarantee that the entire search space is explored, we formalize the mining problem as an incremental graph exploration. Our novel search strategy is coupled with a number of optimization techniques to further prune the search space and efficiently maintain the graph. 
%
Finally, in contrast with traditional ranking of rules based on a measure of support, we propose a new approach inspired by set cover to identify the subset of useful rules to be exposed to the user. 
%
We have conducted extensive experiments using both real-world and synthetic datasets to show that \sys outperform previous proposals in terms of efficiency and that it discovers more effective rules for the application at hand.
\end{abstract}